Energy and exergy analysis of a cruise ship

### 2017-07-19 Manuscript/Manuscript.tex
smhi-data manuscript

Since measurements of ambient and seawater temperature from onboard logging systems were not available for the whole dataset, we used measurements taken from SMHI database for Landsort lighthouse. The assumption was validated based on  June-December period, for which onboard measurements were available. This resulted in a root mean square error of 1.5 K and 1.9 K for the seawater and the ambient temperature respectively, which we considered to be accurate enough for the purpose of this work.
% We did the calculation, resampling the data from SHMI from a 1(3)h to 15min frequency using linear interpolation.

>>>>

Since measurements of ambient and seawater temperature from onboard logging systems were not available for the whole dataset, we used measurements taken from SMHI database for Landsort lighthouse for the seawater, and the lighthouse Svenska Högarna for the ambient temperature. The Landsord lighthouse is situated south of the Stockholm archipelago, and the Svenska Högarna lighthouse is along the ship route, in between the Swedish archipelago and Åland. The assumption was validated based on  June-December period, for which onboard measurements were available. This resulted in a root mean square error of 1.5 K and 1.9 K for the seawater and the ambient temperature respectively, which we considered to be accurate enough for the purpose of this work. The fit the SMHI-data with the rest of the data-set the SMHI data was resampled from 1h for the seawater and 3h for the ambient temperature, to 15min frequency using a linear interpolation.
